Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-14 paper.tex
abstract

\maketitle
\begin{abstract}
Robots are expected to be pervasive in human society in the future

not possible to hardcode everything by hand

requirement for learning

hard to learn for HRI
\begin{itemize}
	\item real time
	\item cost of exploration (real humans)
	\item no clear reward policy and cannot request a human to reward everything
	\item need to make the most out of each sample
\end{itemize}

Partial state RL - accelerate learning

\end{abstract}
%===============================================================================

@@

shaping
guidance

@@

REFORMULATE: start with size of the world and oragnisation by sensory inputs
To be usable in complex environments, a
learning algorithm requires generalisation as exactly identical spaces might
never been observed twice in the life time of the agent.

>>>>

\maketitle
\begin{abstract}
As robots will integrate human society, they will be expected to interact
appropriately with surrounding humans. However at the design time, it cannot be
known in advance exactly all the behaviours expected from the robot, as such to
be accepted in human society robots have to learn how to interact with humans.
Learning social interaction is a complex task, the learning will probably have
to be made online and in the real world, as no simulator precise enough exists.
This means that robots will have to learn directly from interacting with humans,
which limits the quantity of datapoint possible to gather and make exploration
riskier as actions will have real impacts on surrounding humans. Additionally,
no clear reward function exists for social interactions. As such we argue that
robots will highly profit from human expertise and guidance to learn social
interactions and they also will have to make the most out of each datapoint. We
propose to combine the Supervised Progressively Autonomous Robot Competencies
allowing a safer online learning and Reinforcement Learning based on partial
states rather than full states to accelerate the learning, and using more fully
each datapoint.
\end{abstract}
%===============================================================================

@@

shaping \cite{knox2009interactively}

guidance \cite{thomaz2008teachable}

@@

REFORMULATE: start with size of the world and oragnisation by sensory inputs and
focus of attention for human, we can be aware of many things without taking them
into account - more symbolic appraoch?
To be usable in complex environments, a
learning algorithm requires generalisation as exactly identical spaces might
never been observed twice in the life time of the agent.
